On Misuses of the Kolmogorov--Smirnov Test for One Sample Goodness-of-Fit

### 2022-04-28 Manuscript/manuscript.tex
renamed and reordered plots

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_copula_only}
  \caption{Histograms demonstrating copula use to correct dependence.}
  \label{fig:hist_copula_only}
\end{figure}

Figure~\ref{fig:hist_copula_only} displays the results of the copula remedy for dependent data.
The data is generated from an AR-1 model with $\psi = .5$. The copula used is to model
dependence is the normal copula. $1000$ replicate tests were performed with
$B = 1000$ bootstrap samples per test.
\jy{present other scenarios too}
The naive test is performed by simply using the KS test without correcting for any 
potential dependence.

@@

\jy{give a stronger motivation; last section is not practical at all because we
  often don't know the parameters; this section combines the last two}
The remedy using copulas is effective in the case where both assumptions are violated.
This is shown in Figure~\ref{fig:hist_copula}. The ``super naive" method is the resulting 
p-values when you naively use fitted parameters while ignoring dependence in the data.
The ``naive parametric" plot is the result of applying parametric bootstrap to correct
for fitted parameters while ignoring potential dependence. Of course, the "copula" 
plot applies the fix for both assumptions. The results show that copula remedy generates 
uniform p-values and restores the power of the KS test.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_copula}
  \caption{Histograms demonstrating copula use to correct fitted parameters and dependence.}
  \label{fig:hist_copula}
\end{figure}

@@

The copula fix is not a complete solution, because regardless of the true dependence in the data
we assume an AR(1) model by taking the lag-1 sample auto-spearman rho. However, we can 
show that as long as the AR(1) assumption is a close approximation, the correction still restores power to the test.
Figure~\ref{fig:hist_copula_ma1} is the procedure performed on data generated from 
an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_copula_arma} displays results with 
data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_copula_ma1}
  \includegraphics{hist_copula_arma}
  \caption{MA-1 and ARMA(1,1)}
  \label{fig:hist_copula_ma1}
\end{figure}

It is also possible to apply our procedure to other distributions. All of the simulations
to this point have been done with standard normal data. The data in Figure~\ref{fig:hist_copula_gamma} 
is generated from $Gamma ~ (3,1)$ with a correlation coefficient of $\rho = 0.5$. Figure~\ref{fig:hist_copula_gev}
shows the procedure applied to data from $GEV ~ (0, 0.2, 1)$ with a correlation coefficient of $\rho = 0.5$.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_copula_gamma}
  \includegraphics{hist_copula_gev}
  \caption{Gamma(3,1)}
  \label{fig:hist_copula_gamma}
\end{figure}

Where this remedy falls short is when the approximation of an AR-1 dependence 
structure is too inaccurate. An AR-2 model can be used to demonstrate this. For 
an AR-2 model with $\phi = (0.5, 0.3)$, Figure~\ref{fig:hist_copula_ar2} 
displays the results of applying the various remedies. While the remedies 
improve the plot of the p-values in comparison to the naive case, because the 
approximation is not close enough the correction does not work completely.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_copula_ar2}
  \caption{AR-2}
  \label{fig:hist_copula_ar2}
\end{figure}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_ar1_FD}
  \caption{Histograms demonstrating copula use to correct dependence.}
  \label{fig:hist_ar1_FD}
\end{figure}

Figure~\ref{fig:hist_ar1_FD} displays the results of the copula remedy for dependent data.
The data is generated from an AR-1 model with $\psi = .5$. The copula used is to model
dependence is the normal copula. $1000$ replicate tests were performed with
$B = 1000$ bootstrap samples per test.
\jy{present other scenarios too}
The naive test is performed by simply using the KS test without correcting for any 
potential dependence.

@@

\jy{give a stronger motivation; last section is not practical at all because we
  often don't know the parameters; this section combines the last two}
The remedy using copulas is effective in the case where both assumptions are violated.
This is shown in Figure~\ref{fig:hist_ar1_FD}. The ``super naive" method is the resulting 
p-values when you naively use fitted parameters while ignoring dependence in the data.
The ``naive parametric" plot is the result of applying parametric bootstrap to correct
for fitted parameters while ignoring potential dependence. Of course, the "copula" 
plot applies the fix for both assumptions. The results show that copula remedy generates 
uniform p-values and restores the power of the KS test.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_ar1_FD}
  \caption{Histograms demonstrating copula use to correct fitted parameters and dependence.}
  \label{fig:hist_ar1_FD}
\end{figure}

@@

The copula fix is not a complete solution, because regardless of the true dependence in the data
we assume an AR(1) model by taking the lag-1 sample auto-spearman rho. However, we can 
show that as long as the AR(1) assumption is a close approximation, the correction still restores power to the test.
Figure~\ref{fig:hist_ma1_FD} is the procedure performed on data generated from 
an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_arma_FD} displays results with 
data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_ma1_FD}
  \includegraphics{hist_arma_FD}
  \caption{MA-1 and ARMA(1,1)}
  \label{fig:hist_copula_ma1}
\end{figure}

It is also possible to apply our procedure to other distributions. All of the simulations
to this point have been done with standard normal data. The data in Figure~\ref{fig:hist_gamma_FD} 
is generated from $Gamma ~ (3,1)$ with a correlation coefficient of $\rho = 0.5$. Figure~\ref{fig:hist_gev_FD}
shows the procedure applied to data from $GEV ~ (0, 0.2, 1)$ with a correlation coefficient of $\rho = 0.5$.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_gamma_FD}
  \includegraphics{hist_gev_FD}
  \caption{Gamma(3,1)}
  \label{fig:hist_gamma_FD}
\end{figure}

Where this remedy falls short is when the approximation of an AR-1 dependence 
structure is too inaccurate. An AR-2 model can be used to demonstrate this. For 
an AR-2 model with $\phi = (0.5, 0.3)$, Figure~\ref{fig:hist_ar2_FD} 
displays the results of applying the various remedies. While the remedies 
improve the plot of the p-values in comparison to the naive case, because the 
approximation is not close enough the correction does not work completely.

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_ar2_FD}
  \caption{AR-2}
  \label{fig:hist_ar2_FD}
\end{figure}
